Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2014-09-17 Article.tex
update caption

\begin{figure}
 \centering
  \subcaptionbox{$ (\phi, P^{MIN}) $ space\label{fig2:a}}{\includegraphics[width=1.6in]{./figure1/util}}\hspace{1em}%
  \subcaptionbox{$ (N_{COAL}, P^{MIN}) $ space\label{fig2:b}}{\includegraphics[width=1.6in]{./figure6/util2}}
\caption{Utility function in parameters space : In $ (\phi, P^{MIN}) $ when $ N_{COAL} $ is fixed (fig \ref{fig2:a}), and in $ (N_{COAL}, P^{MIN}) $ for a fixed $ \phi $ (fig \ref{fig2:b})}
\label{Fig2}
\end{figure}

>>>>

\begin{figure}
 \centering
  \subcaptionbox{$ (\phi, P^{MIN}) $ subspace\label{fig2:a}}{\includegraphics[width=1.7in]{./figure1/util}}
  \subcaptionbox{$ (N_{COAL}, P^{MIN}) $ subspace\label{fig2:b}}{\includegraphics[width=1.70in]{./figure6/util2}}
\caption{Utility function as function of the parameters space $\{\phi \in [0,1], N_{COAL}\in \mathbb{Z}^+, P^{MIN} \in \mathbb{R}^+\}$: In $ \{\phi, P^{MIN}\} $ when $ N_{COAL} $ is fixed (fig \ref{fig2:a}), and in $ \{N_{COAL}, P^{MIN}\} $ for a fixed $ \phi $ (fig \ref{fig2:b})}
\label{Fig2}
\end{figure}
